### 2014-10-28 LongDataResearchNotes/ARModel.Rmd
Base AR model in place.  Checking for alternate structures

@@

>>>>

summary(LagFormData)

@@

First test regression for hour 19

```{r}
summary(lm(HE~F+LagHE+Weather+LagWeather,data=LagFormData[LagFormData$hour=='19',]   ))
library(lmtest)

dwtest(HE~F+LagHE+Weather+LagWeather,data=LagFormData[LagFormData$hour=='19',])

Looks nice.  Lets do AR
```{r}
library(nlme)
summary(gls(HE~F+LagHE+Weather+LagWeather, data=LagFormData[LagFormData$hour=='19',],corAR1(form=~1),na.action=na.omit))
```

So the action goes away.  Lets assume AR structure is with previous hour and not previous day.  This will take a while to run.  There are a lot of parameters.
```{r}
summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))
```

FULL WIN.  It works.
